Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Minors 2

The objective of this research is to find a set of optimum designs of the specimen previously described according to three different objective functions. These functions are the absorbed energy ($E_a$), the mass of the specimen ($m$) and the peak load ($P_{peak}$). The three metrics are obtained using a finite element simulation, where $E_a$ and $P_{peak}$ are obtained via the force-displacement curves.

@@

Furthermore, other researchers have traditionally swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. Thus, they are also evaluated as objective functions, but considering their more complicated comportment and a noisier nature for this model.

>>>>

The objective functions considered in this research are the absorbed energy ($E_a$), the mass of the specimen ($m$) and the peak load ($P_{peak}$). The mass of the specimen is obtained from the finite element model, and $E_a$ and $P_{peak}$ are obtained from the resulting force-displacement curves.

@@

Furthermore, other researchers have traditionally optimized the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. Thus, they are also evaluated as objective functions, but considering their more complicated comportment and a noisier nature for this model.
